\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section} 
  {\color{RoyalBlue}\large\bfseries}{}{0em}{}[\color{RoyalBlue}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}} 
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% --------- START DOCUMENT ---------
\begin{document}

% ---------- Header ----------
\begin{center}
    {\Huge \scshape Hammadullah Khan} \\ \vspace{1pt}
    \small MERN Stack Developer | Frontend Engineer (React.js) \\ \vspace{1pt}
    Sukkur, Pakistan \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ \href{tel:+923113493754}{\underline{+92 311 3493754}} ~ 
    \href{mailto:hammadkhan394015@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{hammadkhan394015@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/hammadullah-khan}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/hammadullah-khan}} ~
    \href{https://github.com/hammad-se-dev}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/hammad-se-dev}}
\end{center}

% ---------- Summary ----------
\section{Professional Summary}
Enthusiastic React/MERN Stack Developer with hands-on experience building responsive, secure, and high-performance web applications. Proficient in JavaScript (ES6+), React.js, Redux, Context API, and modern UI libraries. Skilled at writing clean, bug-free code, conducting unit tests with 90\%+ coverage, and collaborating in Agile teams. Strong communication skills with ability to analyze requirements, estimate tasks, and deliver scalable solutions aligned with client needs.

% ---------- Skills ----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item \textbf{Frontend:} React.js, Next.js, Redux, Context API, Zustand, HTML5, CSS3, Tailwind CSS
    \item \textbf{UI Libraries:} Material-UI, Chakra UI, Atomize
    \item \textbf{Backend \& APIs:} Node.js, Express.js, RESTful APIs
    \item \textbf{Database:} MongoDB, Supabase
    \item \textbf{Testing:} Jest, React Testing Library (90\%+ coverage)
    \item \textbf{Tools:} Git, GitHub, JIRA, Postman, VS Code, npm/yarn
    \item \textbf{Other:} Agile Development, Responsive Design, Deployment (Netlify, Vercel, Render)
  }
\end{itemize}

% ---------- Experience ----------
\section{Professional Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Spinel Sol (Pvt) Ltd}{Jan 2025 – Present}
    {Frontend Developer}{Karachi/Sukkur, Pakistan}
    \resumeItemListStart
      \resumeItem{Built and maintained React.js applications with Redux/Context API for state management.}
      \resumeItem{Designed user interfaces with Material-UI, ensuring accessibility compliance and responsiveness.}
      \resumeItem{Analyzed business requirements, estimated tasks, and contributed to sprint planning.}
      \resumeItem{Developed reusable components, optimized performance, and applied security best practices.}
      \resumeItem{Implemented unit tests with Jest and React Testing Library, maintaining 90\%+ coverage.}
      \resumeItem{Actively used GitHub and JIRA for version control, issue tracking, and collaboration.}
      \resumeItem{Provided regular status updates to clients and collaborated with cross-functional teams.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% ---------- Projects ----------
\section{Key Projects}
\resumeSubHeadingListStart
  \resumeSubheading
    {Blog App}{Jul 2025 – Aug 2025}
    {Full-stack Blogging Platform}{}
    \resumeItemListStart
      \resumeItem{Developed user authentication, CRUD operations, and protected routes using Next.js and Supabase.}
      \resumeItem{Integrated React Query for data fetching and deployed the app on Render.}
    \resumeItemListEnd

  \resumeSubheading
    {Streamify – Video Chat App}{May 2025 – Jun 2025}
    {Real-time Communication Platform}{}
    \resumeItemListStart
      \resumeItem{Built real-time chat and video calling using MERN stack and GetStream API.}
      \resumeItem{Implemented group messaging, user presence, and responsive UI.}
    \resumeItemListEnd

  \resumeSubheading
    {FYP Management System}{Mar 2025 – Apr 2025}
    {Final Year Project (Full-stack App)}{}
    \resumeItemListStart
      \resumeItem{Developed dashboards for students, supervisors, and committees with rubric-based evaluations.}
      \resumeItem{Implemented project submissions, deadline tracking, and Google Drive integration.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% ---------- Education ----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Sukkur IBA University}{2020 – 2025}
    {Bachelor of Science in Computer Science}{Sukkur, Pakistan}
\resumeSubHeadingListEnd

% ---------- Certifications ----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item Advanced React (Meta) – \href{https://coursera.org/verify/DKFVGNGTDNLS}{Verify}
    \item JavaScript Programming Essentials – \href{https://coursera.org/verify/HV7GT74STZDK}{Verify}
    \item Version Control – \href{https://coursera.org/verify/PDVNWGKQ846S}{Verify}
  }
\end{itemize}

% ---------- Languages ----------
\section{Languages}
English, Urdu

\end{document}
